The Effects of the 2023 Rule Changes in Major League Baseball

### 2023-11-14 manuscript/paper.tex
finished Discussion section of manuscript

What are the main contributions again?

What are the limitations of this study?

What are worth pursuing further in the future?

>>>>

This study provides valuable insights into the immediate effects of the 2023 MLB
rule changes on various baseball statistics. Notably, there is robust evidence
indicating a significant increase in the mean number of stolen bases during the
2023 season. The introduction of a pitch clock and pitcher disengagement limits
appears to have influenced baserunning strategies, fostering a more aggressive
approach on the base paths. Additionally, offensive performance metrics such as
slugging percentage and expected batting average demonstrated significant changes,
suggesting that hitters adapted their approaches to capitalize on the new game dynamics.

However, several limitations should be acknowledged. The study's focus on a single-season
analysis, comparing 2023 to the previous season (2022), provides a snapshot of the
immediate impacts but falls short of capturing potential trends that may have been
happening over multiple seasons. External factors, such as individual player performance,
team strategies, and other influences like basic season to season variation, could have
contributed to observed differences, necessitating a more nuanced examination.
Furthermore, data constraints, particularly the availability of detailed game-level
data for certain metrics, limited the depth of the analysis.

In light of these limitations, future research directions are identified. Long-term
analyses spanning multiple seasons would provide a more comprehensive understanding
of the rule changes' lasting effects. Exploring player-level impacts and variations
across teams could reveal nuanced insights into how individual athletes and teams
adapted to the new rules. Additionally, a broader set of baseball metrics, including
pitcher statistics like Earned Run Average (ERA), and defensive statistics like
Outs Above Average (OAA), could contribute to a more holistic assessment of the rule
changes' impact. Further research assessing fan engagement, satisfaction, and attendance
would enhance our understanding of how these rule changes are perceived by the public.

All in all, while this study sheds light on the immediate impacts, the complex and
dynamic nature of baseball necessitates continuous monitoring and in-depth
analysis to grasp the different effects of rule changes on the sport. The findings
presented here serve as a great starting point for a more nuanced exploration of the
evolving landscape of Major League Baseball.
